Title Goes Here

### 2019-03-30 analysis/paper/paper.Rmd
updates for code, add mmore spatial plots and try animation

ornaments_period <- 
kwl_upper %>% 
  filter(!is.na(`6-layers`)) %>% 
  mutate(period = case_when(
    `6-layers` %in% 1:2 ~ "Chinese Contact",
    `6-layers` == 4 ~ "European Contact",
    `6-layers` %in% 5:6 ~ "Before European Contact",
     TRUE ~ "other"
  )) %>% 
  filter(period != "other")
```

@@

ggplot(transform(ornaments_count,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Categories, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Categories") +
  theme_minimal(base_size = 14)
```

```{r scatter-plot-bead-by-period}
# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Golden bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

ggplot(transform(ornaments_intact_gold,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_point(aes(Length, Width, col = Perforation_average)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Golden beads") +
  coord_fixed(ratio = 1) +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))

# plot for intact glass bead by period
ornaments_intact_glass <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Glass bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1(mm)`, `Perforation2(mm)`), 
                               na.rm = TRUE))

ggplot(transform(ornaments_intact_gold,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_point(aes(Length, Width, col = Perforation_average)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Golden beads") +
  coord_fixed(ratio = 1) +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))

@@

ggplot(transform(agate_bead_shape,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Agate bead") +
  theme_minimal(base_size = 14)

@@

ggplot(transform(bell_shape,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Bell") +
  theme_minimal(base_size = 14)

@@

ggplot(transform(ring_shape,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Metal ring") +
  theme_minimal(base_size = 14)
```

@@

ggplot(transform(ornaments_intact_bell,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_point(aes(Length, Width, col = Type)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Bell") +
  coord_fixed(ratio = 1) +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))

@@

ggplot(transform(ornaments_intact_ring,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_point(aes(Length, Width, col = Type)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Metal ring") +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))
```

@@

# join two dataset to get coordinate
ornaments_period_join <-
  ornaments_period %>%
  mutate(period = as.factor(period)) %>% # seems need this line first 
  group_by(Pit_No, period) %>% 
  count(Categories) %>% 
  inner_join(AD_data, by = c("Pit_No" = "坑號"))

# filter golden bead
ornaments_period_join_gold <-
  ornaments_period_join %>% 
  filter(Categories %in% 'Golden bead')

# plot by period
ggplot(transform(ornaments_period_join_gold,
                 period = factor(period, 
                                     levels = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))) +
  geom_sf(data = sample_units) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n)) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Golden Beads",
       fill = "frequency") +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank())
```

>>>>

ornaments_period <- 
kwl_upper %>% 
  filter(!is.na(`6-layers`)) %>% 
  mutate(period = case_when(
    `6-layers` %in% 1:2 ~ "Chinese Contact",
    `6-layers` == 4 ~ "European Contact",
    `6-layers` %in% 5:6 ~ "Before European Contact",
     TRUE ~ "other"
  )) %>% 
  filter(period != "other") %>% 
  mutate(period = factor(period,
                       level = c("Before European Contact", 
                                                "European Contact", 
                                                "Chinese Contact")))
```

@@

ggplot(ornaments_count) +
  geom_col(aes(Categories, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Categories") +
  theme_minimal(base_size = 14)
```

```{r scatter-plot-bead-by-period}
# plot for intact golden bead by period
ornaments_intact_gold <-
  ornaments_period %>% 
  filter(Condition %in% c('complete', 'near-complete'),
         Categories == 'Golden bead') %>% 
  mutate(Length = as.numeric(`Length(mm)`),
         Thick = as.numeric(`Thick(mm)`),
         Width = as.numeric(`Width(mm)`),
         Perforation1 = as.numeric(`Perforation1(mm)`)) %>% 
  rowwise() %>% 
  mutate(Perforation_average = mean(c(`Perforation1`, `Perforation2(mm)`), 
                               na.rm = TRUE))

ggplot(ornaments_intact_gold) +
  geom_point(aes(Length, Width, col = Perforation_average)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Golden beads") +
  coord_fixed(ratio = 1) +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))

# plot for intact glass bead by period
# need to deal with the original data

@@

ggplot(agate_bead_shape) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Agate bead") +
  theme_minimal(base_size = 14)

@@

ggplot(bell_shape) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Bell") +
  theme_minimal(base_size = 14)

@@

ggplot(ring_shape) +
  geom_col(aes(Type, n)) +
  facet_wrap(~ period) +
  coord_flip() +
  labs(y = "Frequency",
       x = "Shape of Metal ring") +
  theme_minimal(base_size = 14)
```

@@

ggplot(ornaments_intact_bell) +
  geom_point(aes(Length, Width, col = Type)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Bell") +
  coord_fixed(ratio = 1) +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))

@@

ggplot(ornaments_intact_ring) +
  geom_point(aes(Length, Width, col = Type)) +
  facet_wrap(~ period) +
  labs(x = "Length (mm)",
       y = "Width (mm)",
       title = "Metal ring") +
  theme_minimal() +
  theme(plot.title = element_text(hjust=0.5))
```

@@

# join two dataset to get coordinate
ornaments_period_join <-
  ornaments_period %>%
  mutate(period = as.factor(period)) %>% # seems need this line first 
  group_by(Pit_No, period) %>% 
  count(Categories) %>% 
  inner_join(AD_data, by = c("Pit_No" = "坑號"))
```

```{r plot-spatial-distribution}
# filter golden bead
ornaments_period_join_gold <-
  ornaments_period_join %>% 
  filter(Categories %in% 'Golden bead')

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Golden Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

# filter glass bead
ornaments_period_join_gold <-
  ornaments_period_join %>% 
  filter(Categories %in% 'Glass bead')

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Glass Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))

# filter agate bead
ornaments_period_join_gold <-
  ornaments_period_join %>% 
  filter(Categories %in% 'Agate bead')

# plot by period
ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  facet_wrap(~ period) +
  labs(title = "Spatial Distribution of Agate Beads",
       fill = "frequency") +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))
```

```{r-gganimate}
devtools::install_github('thomasp85/gganimate')
library(gganimate)

anim_gold_bead <-
  ggplot(ornaments_intact_gold,
       aes(Length, Width)) +
  geom_point() +
  transition_states(period, 3, 1) +
  labs(title = 'Period: {closest_state}',
       x ='Length (mm) of golden bead',
       y ='Width (mm) of golden bead')

anim_gold_bead_spatial <-
  ggplot(ornaments_period_join_gold) +
  geom_sf(data = sample_units, fill = NA) +
  geom_sf(data = ornaments_period_join_gold, aes(fill = n), alpha = 0.9) +
  transition_states(period, 3, 1) +
  scale_fill_gradient(high = "black", low = "grey") +
  theme_minimal() +
  theme(plot.title = element_text(hjust = 0.5),
        axis.text.x = element_blank(),
        axis.text.y = element_blank(),
        strip.text.x = element_text(size = 11))
